---
output: pdf_document
---
```{r, eval = TRUE, echo = FALSE, message = FALSE}
library(png)
library(grid)
library(gridExtra)
library(xtable)
load("../data/eda-text-output.RData")
```

# Data
The `Credit.csv` dataset consists of `balance` observations (average credit card debt) 
for 400 different individuals, as well as observations for a number of quantitative 
and qualitative variables detailed below: 
  
## Quantitative Variables
* `age`  
* `cards` (number of credit cards)  
* `education` (years of education)  
* `income`(in thousands of dollars)  
* `limit` (credit limit)  
* `rating` (credit rating) 
  
A very general overview of the distribution for each variable is provided in the 
histograms and boxplots below: 

```{r, eval = TRUE, echo = FALSE, message = FALSE}
age_hist <- rasterGrob(as.raster(readPNG("../images/quantitative/histograms/histogram-age.png")), interpolate = FALSE)
age_bp <- rasterGrob(as.raster(readPNG("../images/quantitative/boxplots/boxplot-age.png")), interpolate = FALSE)
balance_hist <- rasterGrob(as.raster(readPNG("../images/quantitative/histograms/histogram-balance.png")), interpolate = FALSE)
balance_bp <- rasterGrob(as.raster(readPNG("../images/quantitative/boxplots/boxplot-balance.png")), interpolate = FALSE)
cards_hist <- rasterGrob(as.raster(readPNG("../images/quantitative/histograms/histogram-cards.png")), interpolate = FALSE)
cards_bp <- rasterGrob(as.raster(readPNG("../images/quantitative/boxplots/boxplot-cards.png")), interpolate = FALSE)
education_hist <- rasterGrob(as.raster(readPNG("../images/quantitative/histograms/histogram-education.png")), interpolate = FALSE)
education_bp <- rasterGrob(as.raster(readPNG("../images/quantitative/boxplots/boxplot-education.png")), interpolate = FALSE)
income_hist <- rasterGrob(as.raster(readPNG("../images/quantitative/histograms/histogram-income.png")), interpolate = FALSE)
income_bp <- rasterGrob(as.raster(readPNG("../images/quantitative/boxplots/boxplot-income.png")), interpolate = FALSE)
limit_hist <- rasterGrob(as.raster(readPNG("../images/quantitative/histograms/histogram-limit.png")), interpolate = FALSE)
limit_bp <- rasterGrob(as.raster(readPNG("../images/quantitative/boxplots/boxplot-limit.png")), interpolate = FALSE)
rating_hist <- rasterGrob(as.raster(readPNG("../images/quantitative/histograms/histogram-rating.png")), interpolate = FALSE)
rating_bp <- rasterGrob(as.raster(readPNG("../images/quantitative/boxplots/boxplot-rating.png")), interpolate = FALSE)

grid.arrange(age_hist,
             age_bp, 
             ncol = 2)
grid.arrange(balance_hist, 
             balance_bp, 
             ncol = 2)
grid.arrange(cards_hist,
             cards_bp,
             ncol = 2)
grid.arrange(education_hist,
             education_bp, 
             ncol = 2)
grid.arrange(income_hist, 
             income_bp, 
             ncol = 2)
grid.arrange(limit_hist,
             limit_bp,
             ncol = 2)
grid.arrange(rating_hist,
             rating_bp,
             ncol = 2)
```

A scatterplot matrix for all quantitative variables and a matrix of correlations are
displayed below:  
```{r, eval = TRUE, echo = FALSE, fig.width = 6, fig.height = 6, fig.align='center'}
matrix <- readPNG("../images/scatterplot-matrix.png")
grid.raster(matrix)
```

```{r, eval = TRUE, echo = FALSE, results = "asis", message = FALSE}
cor_tab <- xtable(quants_cor, 
                  digits = 4,
                  caption = c("Matrix of Correlations for all Quantitative Variables"))
print.xtable(cor_tab, comment = FALSE, caption.placement = "top")
```