---
output: pdf_document
---
#results


## LASSO Regression


```{r, echo=F, warning=F, message=F}
load("../data/lasso-fit.RData")
full_data_lasso_fit <- full_data_fit
```

The LASSO shrunk the predictors Education, Gender, Married, and Ethnicity to zero, leaving Income, Limit, Rating, Cards, Age and Student as significant predictors. The most significant predictor is Limit with a coefficient value of approximately 0.93.

```{r xtable, echo=F, warning=F, message=F, results='asis'}
#cat("LASSO Coefficients /n/n")

#library(xtable)
#coef_table <- xtable(as.matrix(coef(full_data_fit)))
#print(coef_table, type="latex", comment = F, label = "Table 1")
```

## Ridge Regression

```{r, echo=F}
load("../data/ridge-fit.RData")
```



## Principal Component Regression

```{r, echo=F}
load("../data/pcr-fit.RData")
```


## Partial Least Squares Regression

```{r}
load("../data/pls-fit.RData")
validationplot(full_data_pls_fit)
```




## Comparing Methods

coefficient table for all coefficients is here:

```{r, echo=F}
lasso_coef <- coef(full_data_lasso_fit)
pls_coef <- coef(full_data_pls_fit)
pcr_coef <- coef(pcr_full_data_fit)
ridge_coef <- coef(full_data_ridge_fit)

coefficient_matrix <- cbind(ridge_coef[-1,], pcr_coef, pls_coef, as.matrix(lasso_coef)[-1,])
colnames(coefficient_matrix) <- c("Ridge","PCR", "PLS", "LASSO")

```





Table of all the MSE:

Table of the Prediction errors for each train/test model:



